Human Factors Influencing Visual Statistical Inference

### 2015-08-30 sociology_paper.Rnw
updated ip_details.csv
figure 3
re-running models with unordered factors - will change things downstream, but not by much

To explore the significance of the demographic factors model \eqref{eqn:demographic_response} is fit to the data, with age, country, education and gender as fixed effects. To estimate the significance of each of the factors, reduced models are fit with that factor removed from the model. Table ~\ref{tbl:anova_factor} summarizes the results. Except for gender, all of the demographic factors show significant differences in  detection rates.  With respect to time taken, all of the demographic factors are significant.

@@

@@

\cline{3-6} \cline{8-11} 
Factor & Level& Est & SE & Zval & $p$-value && Est & SE & Zval & $p$-value  \\ 
  \hline
\multicolumn{2}{l}{Fixed Effect} &  &  &  &  &  & & && \\ 
&$\mu$ & 3.360 & 0.013 & 249.21 & $<$0.001 &   & -0.683 & 0.071 & -9.64 & $<$0.001 \\ 
\hline
Age ($\alpha$)& 18-25&0.000   &---  &---  &---  &  &--- &--- &---& ---\\   
 &26-30 & 0.058 & 0.013 & 4.50 & $<$0.001 &   & 0.062 & 0.049 & 1.27 & 0.206 \\ 
  &31-35 & 0.068 & 0.014 & 4.72 & $<$0.001 &   & 0.115 & 0.055 & 2.08 & 0.038 \\ 
  &36-40 & 0.231 & 0.016 & 14.05 & $<$0.001 &   & 0.310 & 0.063 & 4.93 & $<$0.001 \\ 
  &41-45 & 0.176 & 0.021 & 8.56 & $<$0.001 &   & 0.158 & 0.081 & 1.96 & 0.050 \\ 
  &46-50 & 0.272 & 0.024 & 11.29 & $<$0.001 &   & 0.141 & 0.096 & 1.47 & 0.143 \\ 
  &above 50 & 0.352 & 0.018 & 19.19 & $<$0.001 &   & 0.147 & 0.071 & 2.06 & 0.039 \\ 
  \hline
Country($\kappa$)& United States&0.000   &---  &---  &---  &  &--- &--- &---& ---\\  
  &India & 0.101 & 0.011 & 9.11 & $<$0.001 &   & 0.058 & 0.043 & 1.33 & 0.183 \\ 
  &Rest of world & -0.129 & 0.009 & -13.82 & $<$0.001 &   & 0.185 & 0.035 & 5.22 & $<$0.001 \\ 
  \hline
Education($\tau$) &High school or less&0.000   &---  &---  &---  &  &--- &--- &---& ---\\     
 &Under grad courses & 0.042 & 0.013 & 3.25 & 0.0011 &   & -0.083 & 0.050 & -1.65 & 0.098 \\ 
  &Under grad degree & -0.037 & 0.012 & -3.21 & 0.0013 &   & -0.044 & 0.045 & -0.97 & 0.331 \\ 
  &Graduate courses & 0.117 & 0.013 & 9.12 & $<$0.001 &   & 0.070 & 0.050 & 1.42 & 0.157 \\ 
  &Graduate degree & 0.046 & 0.011 & 4.12 & $<$0.001 &   & 0.182 & 0.043 & 4.22 & $<$0.001 \\ 
  \hline
Gender ($\gamma$)& Female&0.000   &---  &---  &---  &  &--- &--- &---& ---\\      
  &Male & 0.078 & 0.009 & 8.26 & $<$0.001 &   & 0.055 & 0.036 & 1.50 & 0.133 \\ 
  \hline
\multicolumn{2}{l}{Random Effect} &  &  &  &  &  & & && \\ 
& lineup($\sigma_{\ell}$) & 0.287 &  &  &  &   & 2.293 &  &  &  \\ 
 & Error($\sigma$) & 0.479 & &  &  &  & \mm{? 0.692}&& &\\ 
   \hline
\end{tabular}
}
\label{tbl:model_result_demographics}
\end{table}

>>>>

To explore the significance of the demographic factors model \eqref{eqn:demographic_response} is fit to the data, with age, country, education and gender as fixed effects. To estimate the significance of each of the factors, reduced models are fit with that factor removed from the model. Table~\ref{tbl:anova_factor} summarizes the results. Except for gender, all of the demographic factors show significant differences in  detection rates.  With respect to time taken, all of the demographic factors are significant.

@@

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Sat Aug 29 14:17:22 2015
\begin{table}[hbtp]
\caption{Parameter estimates of models~\eqref{eqn:demographic_time} and~\eqref{eqn:demographic_response} fitted for average log time taken and detection rate, respectively. For time taken all the demographic factors are significant. For detection rate, age group 36-40, rest of the world and graduate degree are significantly different. For gender no difference in performance is observed. Lineup variability is estimated to be very large for model~\eqref{eqn:demographic_response}.}
\centering
\scalebox{.85}{
\begin{tabular}{rrr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}cr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}}
 && \multicolumn{4}{c} {Log Time (model~\ref{eqn:demographic_time})} & &\multicolumn{4}{c} {Detection rate (model~\ref{eqn:demographic_response})}  \\

\cline{3-6} \cline{8-11} 
\multicolumn{2}{c}{{Demographic Factor} \hfill Level} & Est & 2.5\% & 97.5\% &   && Est & 2.5\% & 97.5\% &   \\ 
\cline{3-6} \cline{8-11}
\bf Fixed Effects & Average $\mu$ & 3.16 & 3.12 & 3.20 & *** &   & -0.61 & -0.79 & -0.43 & *** \\ [3pt]
\bf Age Category $(\alpha)$ & 18-25 & \multicolumn{5}{l}{0.00} & \multicolumn{4}{l}{\phantom{-}0.00} \\
&  26-30 & 0.06 & 0.03 & 0.08 & *** &   & 0.06 & -0.03 & 0.16 &  \\ 
&  31-35 & 0.07 & 0.04 & 0.10 & *** &   & 0.11 & 0.01 & 0.22 & * \\ 
&  36-40 & 0.23 & 0.20 & 0.26 & *** &   & 0.31 & 0.19 & 0.43 & *** \\ 
&  41-45 & 0.18 & 0.14 & 0.22 & *** &   & 0.16 & 0.00 & 0.31 & * \\ 
&  46-50 & 0.27 & 0.22 & 0.32 & *** &   & 0.14 & -0.05 & 0.33 &  \\ 
&  above 50 & 0.35 & 0.32 & 0.39 & *** &   & 0.15 & 0.01 & 0.28 & * \\ [3pt]
\bf Country $(\kappa)$& U.S. & \multicolumn{5}{l}{0.00} & \multicolumn{4}{l}{\phantom{-}0.00} \\
&  India & 0.23 & 0.21 & 0.25 & *** &   & -0.18 & -0.27 & -0.10 & *** \\ 
&  Rest of the world & 0.14 & 0.11 & 0.17 & *** &   & 0.08 & -0.04 & 0.20 &  \\ [3pt]
\bf Education $(\tau)$& High School & \multicolumn{5}{l}{0.00} & \multicolumn{4}{l}{\phantom{-}0.00} \\
&  Under grad courses & 0.13 & 0.09 & 0.16 & *** &   & -0.03 & -0.18 & 0.11 &  \\ 
&  Under grad degree & 0.13 & 0.10 & 0.17 & *** &   & 0.12 & -0.01 & 0.26 & . \\ 
&  Graduate courses & 0.01 & -0.04 & 0.05 &  &   & -0.17 & -0.33 & -0.01 & * \\ 
&  Graduate degree & 0.13 & 0.09 & 0.16 & *** &   & -0.06 & -0.19 & 0.07 &  \\ [3pt]
\bf Gender $(\gamma)$& Female & \multicolumn{5}{l}{0.00} & \multicolumn{4}{l}{\phantom{-}0.00} \\
&  Male & 0.08 & 0.06 & 0.10 & *** &   & 0.06 & -0.02 & 0.13 &  \\
\cline{3-6} \cline{8-11}
\bf Random Effects &  lineup $(\sigma_\ell)$& \multicolumn{5}{l}{0.29} & \multicolumn{4}{l}{\phantom{-}2.29} \\ 
                   &  Error $(\sigma)$& \multicolumn{5}{l}{0.69} & \multicolumn{4}{l}{\phantom{-}0.89}  \\ 
\cline{3-6} \cline{8-11}
\end{tabular}}
\end{table}

@@

\cline{3-6} \cline{8-11} 
Factor & Level& Est & SE & Zval & $p$-value && Est & SE & Zval & $p$-value  \\ 
  \hline
\multicolumn{2}{l}{Fixed Effect} &  &  &  &  &  & & && \\ 
&$\mu$ & 3.360 & 0.013 & 249.21 & $<$0.001 &   & -0.683 & 0.071 & -9.64 & $<$0.001 \\ 
\hline
Age ($\alpha$)& 18-25&0.000   &---  &---  &---  &  &--- &--- &---& ---\\   
 &26-30 & 0.058 & 0.013 & 4.50 & $<$0.001 &   & 0.062 & 0.049 & 1.27 & 0.206 \\ 
  &31-35 & 0.068 & 0.014 & 4.72 & $<$0.001 &   & 0.115 & 0.055 & 2.08 & 0.038 \\ 
  &36-40 & 0.231 & 0.016 & 14.05 & $<$0.001 &   & 0.310 & 0.063 & 4.93 & $<$0.001 \\ 
  &41-45 & 0.176 & 0.021 & 8.56 & $<$0.001 &   & 0.158 & 0.081 & 1.96 & 0.050 \\ 
  &46-50 & 0.272 & 0.024 & 11.29 & $<$0.001 &   & 0.141 & 0.096 & 1.47 & 0.143 \\ 
  &above 50 & 0.352 & 0.018 & 19.19 & $<$0.001 &   & 0.147 & 0.071 & 2.06 & 0.039 \\ 
  \hline
Country($\kappa$)& United States&0.000   &---  &---  &---  &  &--- &--- &---& ---\\  
  &India & 0.101 & 0.011 & 9.11 & $<$0.001 &   & 0.058 & 0.043 & 1.33 & 0.183 \\ 
  &Rest of world & -0.129 & 0.009 & -13.82 & $<$0.001 &   & 0.185 & 0.035 & 5.22 & $<$0.001 \\ 
  \hline
Education($\tau$) &High school or less&0.000   &---  &---  &---  &  &--- &--- &---& ---\\     
 &Under grad courses & 0.042 & 0.013 & 3.25 & 0.0011 &   & -0.083 & 0.050 & -1.65 & 0.098 \\ 
  &Under grad degree & -0.037 & 0.012 & -3.21 & 0.0013 &   & -0.044 & 0.045 & -0.97 & 0.331 \\ 
  &Graduate courses & 0.117 & 0.013 & 9.12 & $<$0.001 &   & 0.070 & 0.050 & 1.42 & 0.157 \\ 
  &Graduate degree & 0.046 & 0.011 & 4.12 & $<$0.001 &   & 0.182 & 0.043 & 4.22 & $<$0.001 \\ 
  \hline
Gender ($\gamma$)& Female&0.000   &---  &---  &---  &  &--- &--- &---& ---\\      
  &Male & 0.078 & 0.009 & 8.26 & $<$0.001 &   & 0.055 & 0.036 & 1.50 & 0.133 \\ 
  \hline
\multicolumn{2}{l}{Random Effect} &  &  &  &  &  & & && \\ 
& lineup($\sigma_{\ell}$) & 0.287 &  &  &  &   & 2.293 &  &  &  \\ 
 & Error($\sigma$) & 0.692 & &  &  &  & 0.893 && &\\ 
   \hline
\end{tabular}
}
\label{tbl:model_result_demographics}
\end{table}
